
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage[numbers]{natbib}

\geometry{margin=1in}

\title{## Novel Deep Learning Approach for Image Classification}
\author{}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This paper presents a novel deep learning approach for image classification that achieves state-of-the-art performance on multiple benchmark datasets. Our method combines convolutional neural networks with attention mechanisms to improve feature extraction and classification accuracy. Experimental results demonstrate significant improvements over existing methods, with accuracy gains of up to 5% on standard datasets. The proposed approach is computationally efficient and can be deployed on resou
\end{abstract}

\section*{Introduction}
No Introduction section found.

\section*{Methods}
No Methods section found.

\section*{Results}
No Results section found.

\section*{Discussion}
No Discussion section found.

\section*{References}
\begin{thebibliography}{99}
\bibitem{1} 1. Smith, J. et al. Deep learning for image classification. Nature 2020, 580, 123-126. [2] Johnson, A. &amp; Brown, B. Attention mechanisms in neural networks. Science 2021, 372, 145-149. [3] Zhang, C. et al. Efficient deep learning architectures. IEEE Transactions 2022, 45, 78-92. [4] Chen, D. et al. Convolutional neural networks for visual recognition. ACM Computing Surveys 2023, 55, 1-35.

\end{thebibliography}

\section*{Formatting Changes Log}
\textbf{metadata_title_case:} '## Novel Deep Learning Approach for Image Classification' $\rightarrow$ '## Novel Deep Learning Approach For Image Classification' (IEEE requires Title Case) \\
\textbf{section_order:} Introduction $\rightarrow$ I. INTRODUCTION (IEEE requires section structure: I. INTRODUCTION, II. METHODOLOGY, III. RESULTS, IV. DISCUSSION, V. CONCLUSION, REFERENCES) \\
\textbf{section_order:} Results $\rightarrow$ III. RESULTS (IEEE requires section structure: I. INTRODUCTION, II. METHODOLOGY, III. RESULTS, IV. DISCUSSION, V. CONCLUSION, REFERENCES) \\
\textbf{section_order:} Discussion $\rightarrow$ IV. DISCUSSION (IEEE requires section structure: I. INTRODUCTION, II. METHODOLOGY, III. RESULTS, IV. DISCUSSION, V. CONCLUSION, REFERENCES) \\


\end{document}
